fGFPCA dynamic prediction

### 2023-02-24 f-GFPCA.Rmd
some formatting

This is a bit more complicated. The full compuation time consists of two parts: 
- Time spent on model fitting
- Time spent on prediction **given** the fitted FPCA or adaptive GLMM models.

>>>>

This is a bit more complicated. The full computation time consists of two parts:

- Time spent on model fitting
- Time spent on prediction **given** the fitted FPCA or adaptive GLMM models

Table below include time spent only for prediction.
